{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-01 thesis/landslide.tex
fix citations to be colorful insted of having ugly borders

\begin{itemize}
\item {\bf Search algorithm options}
\begin{itemize}
	\item {\tt ICB=0} - enable Iterative Context Bounding (\sect{\ref{sec:landslide-icb}});
		corresponds to {\tt -I} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt PREEMPT\_EVERYWHERE=0} - enable Preempt-Everywhere mode (\sect{\ref{sec:quicksand-eval}});
		corresponds to {\tt -0} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt EXPLORE\_BACKWARDS=0} - configure whether, at each newly encountered preemption point,
		to allow the current thread to run first then later upon backtracking to preempt (0),
		or to issue preemptions first and then try continuing the current thread later (1).
		0 tends to produce shorter preemption traces while 1 tends to find bugs faster (\cite{landslide} \S{}8.7.1).
		Not compatible with ICB.
\end{itemize}

@@

		\footnote{This option replaces the deprecated {\tt kern\_current\_extra\_runnable()} annotation from {\tt student.c} described in \cite{landslide} \S{}6.2.3.}

@@

{\tt check\_withins()} implements the allow/denylist behaviour for the former two of those commands
(in a similar manner to the Preemption Sealing technique described in prior work \cite{sealing}).
It invokes the stack tracer (\sect{\ref{sec:landslide-stacktrace}})
for a list of which functions are on the call stack
(hence the importance of the stack tracer's complex logic to not miss any frames
even when interrupts or system calls are involved).
Then, to determine if the current program state should be considered a valid preemption point,
or whether it should be rejected,
it compares each {\tt within} or {\tt without\_function} directive in the following sequence-dependent manner:

>>>>

\begin{itemize}
\item {\bf Search algorithm options}
\begin{itemize}
	\item {\tt ICB=0} - enable Iterative Context Bounding (\sect{\ref{sec:landslide-icb}});
		corresponds to {\tt -I} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt PREEMPT\_EVERYWHERE=0} - enable Preempt-Everywhere mode (\sect{\ref{sec:quicksand-eval}});
		corresponds to {\tt -0} in \sect{\ref{sec:landslide-quicksand-options}}.
	\item {\tt EXPLORE\_BACKWARDS=0} - configure whether, at each newly encountered preemption point,
		to allow the current thread to run first then later upon backtracking to preempt (0),
		or to issue preemptions first and then try continuing the current thread later (1).
		0 tends to produce shorter preemption traces while 1 tends to find bugs faster (\cite[\S{}8.7.1]{landslide}).
		Not compatible with ICB.
\end{itemize}

@@

		\footnote{This option replaces the deprecated {\tt kern\_current\_extra\_runnable()} annotation from {\tt student.c} described in \cite[\S{}6.2.3]{landslide}.}

@@

{\tt check\_withins()} implements the allow/denylist behaviour for the former two of those commands
(in a similar manner to \revisionminor{prior work's Preemption Sealing} \cite{sealing}).
It invokes the stack tracer (\sect{\ref{sec:landslide-stacktrace}})
for a list of which functions are on the call stack
(hence the importance of the stack tracer's complex logic to not miss any frames
even when interrupts or system calls are involved).
Then, to determine if the current program state should be considered a valid preemption point,
or whether it should be rejected,
it compares each {\tt within} or {\tt without\_function} directive in the following sequence-dependent manner:
